---
title: "Draft Quarto document"
author: "Your Name"
format: html
---

## Header 1
Whenever it has setup in the chunk name, it will automatically run in the beginning
```{r setup}
library(tidyverse)
library(here)
library(fs)
library(lubridate)
source(here("R/functions.R"))
```

## Importing new data
Use the _ version of read csv and not the .
```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, n_max = 100
  )
```

## Exercise: Reading other files
```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712//HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, n_max = 100
  )
```


```{r}
#| eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712//HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```


```{r}
#| eval: false
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, n_max = 100
  )
```


```{r}
#| eval: false
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```

## Making a function to add numbers

```{r}
#' Add two numbers together.
#'
#' @param num1 A number here
#' @param num2 A number here
#'
#' @returns Returns the sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

## Make a function that loads the data

```{r}
#| eval: false
#' Read in one nurses stress data file
#'
#' @param file_path A path to a data file
#'
#' @returns Outputs a dataframe /tibble
read <- function(file_path) {
  data <- file_path %>%
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case, n_max = 100
    )
  return(data)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>% read()
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>% read()
```

## Exercise 16.7

```{r}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 10)

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

## Using map
dir_ls : Lists all the files in a specific folder. Below we list all the files in the folder that are relevant for us to read. recurse = TRUE - this is because they are not all stored in the same folder. 
```{r}
hr_files <- here("data-raw/nurses-stress/") %>%
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files
```

Herunder binder vi rækkerne med data sammen og giver id nummer
```{r}
hr_data <- hr_files %>%
  map(read) %>% # no brackets
  list_rbind(names_to = "file_path_id")
```

## Exercise: Convert map to function and use on sleep

Make a function that reads in all datasets
```{r}
#| eval: false
#' Read in all data
#'
#' @param filename List of relevant files
#'
#' @returns Data
read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") %>%
    fs::dir_ls(regexp = filename, recurse = TRUE)

  data <- files %>%
    map(read) %>%
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}
```

```{r}
hr_data <- read_all("HR.csv.gz")
ibi_data <- read_all("IBI.csv.gz")
bvp_data <- read_all("BVP.csv.gz")
```

## Inspecting the data

```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") %>% read()
```

## Extract ID
```{r}
hr_data %>%
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) %>%
      str_remove("/stress/") %>%
      str_remove("/"),
    .before = file_path_id
  ) %>%
  select(-file_path_id)
```


## 19.7 Exercise 

```{r}
#| eval: false
#' Get the IDs
#'
#' @param data List the dataset that you want to extract ID from
#'
#' @returns Document with correct ID

get_participant_id <- function(data) {
  id <- data %>%
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) %>%
        stringr::str_remove("/stress/") %>%
        stringr::str_remove("/"),
      .before = file_path_id
    ) %>%
    dplyr::select(-file_path_id)

  return(id)
}
```

```{r}
get_participant_id(hr_data)
```

## Working with across

```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id()
```

```{r}
hr_data %>%
  summarise(across(where(is.numeric), list(
    mean = mean,
    median = median,
    sd = sd
  )))
```

## Working with dates

```{r}
hr_data %>%
  mutate(
    datetime = round_date(collection_datetime,
      unit = "minute"
    ),
    .before = "collection_datetime"
  )
```

## Summarising by groups

```{r}
hr_data %>%
  mutate(
    collection_datetime = round_date(
      collection_datetime,
      unit = "minute"
    )
  ) %>%
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime)
  )
```
